A Study of Immersion Factors Using an Augmented Reality Simulation

### 2009-06-24 trunk/Paper/paper.tex

\begin{abstract}
This is a study using a virtual reality (VR) simulation system to examine the effects of various problems associated with augmented reality (AR). In a second study using the AR simulator, we studied a tracking task where the AR interface provides x-ray vision to help track a moving target.  We varied the field of view of the AR display, as well as the reliability of the head tracker.  In low reliability conditions, we simulate tracker failure by disabling the augmented view of the scene for brief periods.  Our study gives insight into the effect of head tracker reliability on user performance in a tracking task, as well as the relationship between reliability and field of view in an AR system.

@@

\section*{Acknowledgements}

>>>>

\begin{abstract}

Augmented reality (AR) systems are expensive.  It is worth studying the effects of level of immersion in AR systems in order to determine an appropriate cost to benefit ration.  This is an AR study, simulated using a virtual reality (VR), to examine the effects of level of immersion in AR.  We analyze a tracking task where the AR interface provides x-ray vision to help track a moving target.  We varied the field of view of the AR display, as well as the reliability of the head tracker.  In low reliability conditions, we simulate tracker failure by disabling the augmented view of the scene for brief periods.  Our study gives insight into the effect of head tracker reliability on user performance in a tracking task, as well as the relationship between reliability and field of view in an AR system.

@@

\section*{Acknowledgements}
Cha Lee, Steffan Gauglitz, funding, and all of our participants.
